---
title: "Happiness Deciphered!"
author: "Zauad Shahreer Abeer"
date: "October 16, 2018"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

## Happiness in the making

The **World Happiness Report**, published by the UN Sustainable Development Solutions Network, gives the rankings of different countries happiness based on people's assessments of their well-being in Gallup World Poll surveys. The top nations, the report says, "tend to have high values for the key variables that have been found to support well-being: income, healthy life expectancy, social support, freedom, trust and generosity."  

Let us play with the World Happiness data and make some visualizations to see how the key variables affect happiness.  



## The visualization {.smaller}

```{r}
source("./script.R")

#plotting
make_plot()
```

  
  
**Dimensions:**  
x-axis: GDP per capita (log scale),  
y-axis: happiness_score (scale of 1-10),  
color: freedom of choice (scale of 1-10),  
size: avg. life expectancy at birth (in years).  



## Discussions

We can see an increasing pattern of happiness with GDP. This says that happiness is indeed related to income.  
Again, we see a large number of yellows at the top right corner, indicating that countries with more freedom are more happy.  
Finally, the size tends to increase as we go up, which tells us that happiness increases with average life expectency.  

Thus, we see that countries with more income, better health and more freedom are happy countries.  Of course this is by no means an exhaustive list, the term happiness is one of the deepest term in the history of mankind and cannot be explained by three factors only. This is just the start.  

## References {.smaller}

1. Data collected from [World Happiness Report 2018](http://worldhappiness.report/ed/2018/)